---
title: ""
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: false
header-includes:
  - \usepackage{geometry}
  - \geometry{margin=0.9in}
  - \usepackage{xcolor}
  - \definecolor{navy}{HTML}{0b172a}
  - \definecolor{teal}{HTML}{2EC4B6}
  - \definecolor{purple}{HTML}{8E44AD}
  - \definecolor{blue}{HTML}{4a91e2}
  - \definecolor{coral}{HTML}{f2615a}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[L]{\textcolor{teal}{\textbf{E-Breathomics}}}
  - \fancyhead[R]{\textcolor{teal}{Clinical Report}}
  - \fancyfoot[C]{\textcolor{gray}{\thepage}}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\headrule}{\hbox to\headwidth{\color{teal}\leaders\hrule height \headrulewidth\hfill}}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
params:
  mode: "cohort"
  report_date: NULL
  patient_id: NULL
  patient_info: NULL
  cohort_summary: NULL
  alpha_df: NULL
  cohort_alpha_df: NULL
  pcoa_data: NULL
  permanova_diag: NULL
  permanova_type: NULL
  tax_df: NULL
  top_species_df: NULL
  drug_resistance_df: NULL
  full_arg_df: NULL
  vf_df: NULL
  mge_df: NULL
  patho_mat: NULL
  patho_ann: NULL
  ge_summary_df: NULL
  patient_table: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", fig.pos = "H",
  dev = "cairo_pdf"
)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
library(pheatmap)
library(grid)

# E-Breathomics colour palette
eb_navy   <- "#0b172a"
eb_teal   <- "#2EC4B6"
eb_blue   <- "#4a91e2"
eb_purple <- "#8E44AD"
eb_cream  <- "#FAF0E6"
eb_coral  <- "#f2615a"

ip_palette     <- c(CVID = "#4a91e2", XLA = "#009e74", HG = "#8c57b4", SID = "#d55e00")
sample_palette <- c(Exhale = "#93e9f5", Sputum = "#fcf260")

eb_theme <- theme_minimal(base_size = 11) +
  theme(
    plot.background   = element_rect(fill = eb_navy, colour = NA),
    panel.background  = element_rect(fill = eb_navy, colour = NA),
    panel.grid.major  = element_line(colour = "#1a2f4e", linewidth = 0.3),
    panel.grid.minor  = element_blank(),
    text              = element_text(colour = eb_cream),
    axis.text         = element_text(colour = eb_cream, size = 9),
    axis.title        = element_text(colour = eb_cream, size = 10),
    plot.title        = element_text(colour = eb_teal, face = "bold", size = 13),
    plot.subtitle     = element_text(colour = eb_cream, size = 9),
    legend.background = element_rect(fill = eb_navy, colour = NA),
    legend.text       = element_text(colour = eb_cream, size = 8),
    legend.title      = element_text(colour = eb_teal, size = 9),
    strip.text        = element_text(colour = eb_cream, size = 9),
    plot.margin       = margin(10, 10, 10, 10)
  )

is_cohort <- params$mode == "cohort"
```

\begin{center}
{\Huge\textcolor{teal}{\textbf{`r if (is_cohort) "Cohort Analysis Report" else "Clinical Patient Report"`}}}

\vspace{0.3cm}
{\large Report generated on `r params$report_date`}

`r if (!is_cohort) paste0("\\vspace{0.1cm}\n{\\small Research ID: \\textbf{", params$patient_id, "}}")`
\end{center}

\vspace{0.3cm}
\noindent\textcolor{teal}{\rule{\textwidth}{1pt}}

<!-- ================================================================== -->
<!-- COHORT MODE -->
<!-- ================================================================== -->

```{r cohort_guard, eval=is_cohort, results='asis'}
cat("")
```

`r if (is_cohort) '# 1. Cohort Demographics'`

```{r cohort_demographics, eval=is_cohort}
cs <- params$cohort_summary

demo_df <- data.frame(
  Metric = c("Total Patients", "Diagnoses",
             "Sex Distribution", "Age Range"),
  Value = c(
    as.character(cs$n_patients),
    paste(names(cs$diag_counts), cs$diag_counts, sep = ": ", collapse = " | "),
    paste(names(cs$sex_counts), cs$sex_counts, sep = ": ", collapse = " | "),
    paste0(cs$age_range[1], " - ", cs$age_range[2], " years (mean: ", cs$age_mean, ")")
  )
)

kable(demo_df, col.names = c("", ""), booktabs = TRUE, align = c("l", "l"))
```

```{r cohort_diag_bar, eval=is_cohort, fig.width=6, fig.height=3, out.width="85%"}
cs <- params$cohort_summary

diag_df <- data.frame(
  Diagnosis = names(cs$diag_counts),
  Count = as.numeric(cs$diag_counts)
)

ggplot(diag_df, aes(x = reorder(Diagnosis, Count), y = Count, fill = Diagnosis)) +
  geom_col(width = 0.6) +
  scale_fill_manual(values = ip_palette) +
  coord_flip() +
  labs(title = "Patient Distribution by Diagnosis", x = NULL, y = "Number of Patients") +
  eb_theme + theme(legend.position = "none")
```

`r if (is_cohort) '# 2. Alpha Diversity Comparison'`

```{r cohort_alpha_box, eval=is_cohort, fig.width=7, fig.height=4, out.width="100%"}
df <- params$alpha_df

if (nrow(df) > 0) {
  # Richness boxplot
  kw_rich <- kruskal.test(Richness ~ Immunodeficiency_diagnosis, data = df)
  kw_shan <- kruskal.test(Shannon ~ Immunodeficiency_diagnosis, data = df)

  p1 <- ggplot(df, aes(x = Immunodeficiency_diagnosis, y = Richness,
                        fill = Immunodeficiency_diagnosis)) +
    geom_boxplot(width = 0.5, outlier.colour = eb_coral) +
    scale_fill_manual(values = ip_palette) +
    labs(title = "Richness by Diagnosis",
         subtitle = paste("Kruskal-Wallis p =", format(kw_rich$p.value, digits = 3)),
         x = NULL, y = "Richness") +
    eb_theme + theme(legend.position = "none")

  p2 <- ggplot(df, aes(x = Immunodeficiency_diagnosis, y = Shannon,
                        fill = Immunodeficiency_diagnosis)) +
    geom_boxplot(width = 0.5, outlier.colour = eb_coral) +
    scale_fill_manual(values = ip_palette) +
    labs(title = "Shannon Index by Diagnosis",
         subtitle = paste("Kruskal-Wallis p =", format(kw_shan$p.value, digits = 3)),
         x = NULL, y = "Shannon Index") +
    eb_theme + theme(legend.position = "none")

  gridExtra::grid.arrange(p1, p2, ncol = 2)
}
```

```{r cohort_alpha_text, eval=is_cohort, results='asis'}
if (nrow(params$alpha_df) > 0) {
  kw <- kruskal.test(Shannon ~ Immunodeficiency_diagnosis, data = params$alpha_df)
  sig <- if (kw$p.value < 0.05) "statistically significant" else "not statistically significant"
  cat(paste0(
    "The Kruskal-Wallis test indicates that differences in Shannon diversity ",
    "across diagnosis groups are **", sig, "** (p = ",
    format(kw$p.value, digits = 3), ")."
  ))
}
```

`r if (is_cohort) '# 3. Beta Diversity (PCoA)'`

```{r cohort_pcoa, eval=is_cohort, fig.width=7, fig.height=5, out.width="100%"}
pd <- params$pcoa_data

if (!is.null(pd) && nrow(pd$pcoa_df) > 0) {
  ve <- pd$var_expl

  ggplot(pd$pcoa_df, aes(x = PC1, y = PC2,
                          colour = Immunodeficiency_diagnosis)) +
    geom_point(size = 2.5, alpha = 0.8) +
    stat_ellipse(linewidth = 0.8, linetype = "dashed") +
    scale_colour_manual(values = ip_palette) +
    labs(
      title = "PCoA - Bray-Curtis Dissimilarity (Hellinger transformed)",
      x = paste0("PC1 (", round(ve[1], 1), "%)"),
      y = paste0("PC2 (", round(ve[2], 1), "%)"),
      colour = "Diagnosis"
    ) +
    eb_theme
}
```

```{r cohort_permanova, eval=is_cohort, results='asis'}
if (!is.null(params$permanova_diag)) {
  cat("**PERMANOVA — by Diagnosis:**\n\n")
  perm_d <- params$permanova_diag
  cat(paste0(
    "- R\u00b2 = ", round(perm_d$R2[1], 4),
    ", F = ", round(perm_d$F[1], 2),
    ", p = ", perm_d$`Pr(>F)`[1], "\n\n"
  ))
}

if (!is.null(params$permanova_type)) {
  cat("**PERMANOVA — by Sample Type:**\n\n")
  perm_t <- params$permanova_type
  cat(paste0(
    "- R\u00b2 = ", round(perm_t$R2[1], 4),
    ", F = ", round(perm_t$F[1], 2),
    ", p = ", perm_t$`Pr(>F)`[1], "\n\n"
  ))
}
```

`r if (is_cohort) '# 4. Taxonomic Profiles'`

```{r cohort_tax_cvid, eval=is_cohort, fig.width=8, fig.height=7.5, out.width="100%"}
tax <- params$tax_df

if (!is.null(tax) && nrow(tax) > 0) {
  n_genera <- length(unique(tax$genus))
  pal <- paletteer::paletteer_d("ggsci::default_igv", n = min(n_genera, 51))

  tax_cvid  <- tax %>% filter(Immunodeficiency_diagnosis == "CVID")
  tax_other <- tax %>% filter(Immunodeficiency_diagnosis != "CVID")

  shared_theme <- eb_theme +
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1, size = 6),
      legend.position = "none"
    )

  p1 <- ggplot(tax_cvid, aes(x = sample, y = Percentage, fill = genus)) +
    geom_bar(stat = "identity") +
    facet_grid(. ~ ID, scales = "free_x", space = "free") +
    scale_fill_manual(values = pal) +
    labs(title = "CVID", x = NULL, y = "Rel. Abundance (%)", fill = "Genus") +
    shared_theme

  p2 <- ggplot(tax_other, aes(x = sample, y = Percentage, fill = genus)) +
    geom_bar(stat = "identity") +
    facet_grid(. ~ Immunodeficiency_diagnosis + ID,
               scales = "free_x", space = "free") +
    scale_fill_manual(values = pal) +
    labs(title = "Other Diagnoses", x = NULL, y = "Rel. Abundance (%)", fill = "Genus") +
    shared_theme +
    theme(legend.position = "bottom",
          legend.key.size = unit(0.25, "cm"),
          legend.text = element_text(size = 5, colour = eb_cream),
          legend.title = element_text(size = 6, colour = eb_teal)) +
    guides(fill = guide_legend(nrow = 3, title.position = "top"))

  gridExtra::grid.arrange(p1, p2, nrow = 2, heights = c(1, 1.3),
                           top = grid::textGrob("Relative Abundance by Diagnosis",
                                                gp = grid::gpar(col = eb_teal,
                                                                 fontsize = 13,
                                                                 fontface = "bold")))
}
```

```{r cohort_tax_table, eval=is_cohort}
if (!is.null(params$tax_df) && nrow(params$tax_df) > 0) {
  tax_summary <- params$tax_df %>%
    group_by(genus, Immunodeficiency_diagnosis) %>%
    summarise(Mean_Abundance = round(mean(Percentage, na.rm = TRUE), 2),
              .groups = "drop") %>%
    pivot_wider(names_from = Immunodeficiency_diagnosis,
                values_from = Mean_Abundance, values_fill = 0) %>%
    arrange(desc(rowMeans(select(., -genus), na.rm = TRUE))) %>%
    slice_head(n = 10)

  kable(tax_summary, booktabs = TRUE, align = c("l", rep("c", ncol(tax_summary) - 1)),
        caption = "Top 10 genera — mean relative abundance (\\%) by diagnosis")
}
```

`r if (is_cohort) '# 5. Pathogenomics Summary'`

```{r cohort_heatmap, eval=is_cohort, fig.width=8, fig.height=6, out.width="100%"}
mat <- params$patho_mat
ann <- params$patho_ann

if (!is.null(mat) && nrow(mat) > 0 && ncol(mat) > 0) {
  ann_colors <- list(
    type = sample_palette,
    Immunodeficiency_diagnosis = ip_palette
  )

  pheatmap(
    mat,
    cluster_cols   = FALSE,
    cluster_rows   = FALSE,
    scale          = "none",
    color          = colorRampPalette(c(eb_navy, eb_teal, eb_coral))(50),
    border_color   = NA,
    annotation_col = ann,
    annotation_colors = ann_colors,
    fontsize_row   = 7,
    fontsize_col   = 7,
    fontsize       = 9,
    main           = "Gene Abundance (log TPM) - Top Genes"
  )
}
```

```{r cohort_arg_summary, eval=is_cohort}
if (!is.null(params$drug_resistance_df) && nrow(params$drug_resistance_df) > 0) {
  arg_by_diag <- params$drug_resistance_df %>%
    group_by(Immunodeficiency_diagnosis) %>%
    summarise(
      N_Species_with_ARGs = n_distinct(name),
      Total_ARGs = sum(n_ARGs),
      Drug_Classes = paste(sort(unique(na.omit(unlist(str_split(Drug_Classes, ", "))))),
                           collapse = ", "),
      .groups = "drop"
    )

  kableExtra::kbl(arg_by_diag, booktabs = TRUE,
        col.names = c("Diagnosis", "Species\nwith ARGs", "Total\nARGs", "Drug Resistance Classes"),
        caption = "Antibiotic resistance gene summary by diagnosis") %>%
    kableExtra::column_spec(1, width = "2cm") %>%
    kableExtra::column_spec(2, width = "2cm") %>%
    kableExtra::column_spec(3, width = "1.5cm") %>%
    kableExtra::column_spec(4, width = "9cm")
}
```

```{r cohort_ge_table, eval=is_cohort}
if (!is.null(params$ge_summary_df) && nrow(params$ge_summary_df) > 0) {
  kable(params$ge_summary_df %>% select(Category, `Genes Detected` = n_genes),
        booktabs = TRUE, caption = "Genetic elements detected across cohort")
}
```

`r if (is_cohort) '\\newpage'`

`r if (is_cohort) '# 6. Per-Patient Summary'`

```{r cohort_patient_table, eval=is_cohort}
if (!is.null(params$patient_table) && nrow(params$patient_table) > 0) {
  kable(params$patient_table, booktabs = TRUE, longtable = TRUE, align = c("c","l","c","c","c","c","c","c"),
        caption = "Individual patient summary")
}
```

<!-- ================================================================== -->
<!-- INDIVIDUAL MODE -->
<!-- ================================================================== -->

```{r indiv_guard, eval=!is_cohort, results='asis'}
cat("")
```

`r if (!is_cohort) '# 1. Patient Demographics'`

```{r indiv_demographics, eval=!is_cohort}
info <- params$patient_info

if (!is.null(info)) {
  patient_df <- data.frame(
    Field = c("Research ID", "Age", "Sex", "Immunodeficiency Diagnosis",
              "Treatment", "Immunocompromised Type",
              "Samples Analysed", "Sample Types"),
    Value = c(
      as.character(info$id),
      paste0(info$age, " years"),
      info$sex,
      info$diagnosis,
      info$treatment,
      info$immuno_type,
      as.character(info$n_samples),
      info$sample_types
    )
  )

  kable(patient_df, col.names = c("", ""), booktabs = TRUE, align = c("l", "l"))
}
```

`r if (!is_cohort) '# 2. Species Profile'`

```{r indiv_species_bar, eval=!is_cohort, fig.width=7, fig.height=5, out.width="100%"}
df <- params$top_species_df

if (!is.null(df) && nrow(df) > 0) {
  n <- nrow(df)
  bar_colours <- colorRampPalette(c(eb_teal, eb_blue, eb_purple))(n)

  ggplot(df, aes(x = reorder(Species, Total_Count), y = Total_Count)) +
    geom_col(fill = rev(bar_colours), width = 0.7) +
    coord_flip() +
    scale_y_log10(labels = scales::comma_format()) +
    labs(
      title = "Top Species by Read Count",
      subtitle = paste0("Showing top ", n, " species"),
      x = NULL, y = "Total Count (log scale)"
    ) +
    eb_theme
}
```

```{r indiv_species_table, eval=!is_cohort}
if (!is.null(params$top_species_df) && nrow(params$top_species_df) > 0) {
  species_tbl <- params$top_species_df %>%
    select(Species, `Total Count` = Total_Count) %>%
    mutate(`Relative %` = round(`Total Count` / sum(`Total Count`) * 100, 1))

  kable(species_tbl, booktabs = TRUE, align = c("l", "r", "r"),
        caption = "Species abundance profile")
}
```

`r if (!is_cohort) '# 3. Antibiotic Resistance Genes'`

```{r indiv_arg_table, eval=!is_cohort}
if (!is.null(params$full_arg_df) && nrow(params$full_arg_df) > 0) {
  arg_display <- params$full_arg_df %>%
    select(Species, Gene = GENE, `Resistance Class` = RESISTANCE,
           TPM) %>%
    mutate(TPM = round(TPM, 1),
           `Resistance Class` = gsub(";", "; ", `Resistance Class`)) %>%
    arrange(Species, desc(TPM))

  kableExtra::kbl(arg_display, booktabs = TRUE, longtable = TRUE,
        caption = "Complete ARG profile — genes detected via CARD database") %>%
    kableExtra::column_spec(1, width = "2.5cm") %>%
    kableExtra::column_spec(2, width = "2.5cm") %>%
    kableExtra::column_spec(3, width = "8cm") %>%
    kableExtra::column_spec(4, width = "1.5cm")
} else {
  cat("*No antibiotic resistance genes were detected.*\n")
}
```

```{r indiv_drug_bar, eval=!is_cohort, fig.width=7, fig.height=4, out.width="100%"}
if (!is.null(params$drug_resistance_df) && nrow(params$drug_resistance_df) > 0) {
  drug_classes <- params$drug_resistance_df %>%
    tidyr::separate_rows(Drug_Classes, sep = ", ") %>%
    group_by(Drug_Classes) %>%
    summarise(n_genes = sum(n_ARGs), .groups = "drop") %>%
    filter(Drug_Classes != "") %>%
    arrange(desc(n_genes))

  if (nrow(drug_classes) > 0) {
    ggplot(drug_classes, aes(x = reorder(Drug_Classes, n_genes), y = n_genes)) +
      geom_col(fill = eb_coral, width = 0.7) +
      coord_flip() +
      labs(
        title = "Drug Resistance Classes",
        subtitle = "Number of ARGs per antibiotic class",
        x = NULL, y = "Number of ARGs"
      ) +
      eb_theme
  }
}
```

```{r indiv_species_arg_xref, eval=!is_cohort}
if (!is.null(params$drug_resistance_df) && nrow(params$drug_resistance_df) > 0) {
  xref <- params$drug_resistance_df %>%
    select(Species, `N ARGs` = n_ARGs, `Drug Classes` = Drug_Classes)

  kable(xref, booktabs = TRUE, align = c("l", "c", "l"),
        caption = "Species carrying antibiotic resistance genes")
}
```

`r if (!is_cohort) '# 4. Virulence Factors & Mobile Genetic Elements'`

```{r indiv_vf_table, eval=!is_cohort}
if (!is.null(params$vf_df) && nrow(params$vf_df) > 0) {
  kable(params$vf_df %>% select(Species, Gene = GENE, TPM) %>%
          mutate(TPM = round(TPM, 1)) %>% arrange(Species, desc(TPM)),
        booktabs = TRUE, longtable = TRUE,
        caption = "Virulence factors detected (VFDB)")
} else {
  cat("*No virulence factors detected.*\n\n")
}
```

```{r indiv_mge_table, eval=!is_cohort}
if (!is.null(params$mge_df) && nrow(params$mge_df) > 0) {
  kable(params$mge_df %>% select(Species, Gene = GENE, TPM) %>%
          mutate(TPM = round(TPM, 1)) %>% arrange(Species, desc(TPM)),
        booktabs = TRUE, longtable = TRUE,
        caption = "Mobile genetic elements detected (PlasmidFinder)")
} else {
  cat("*No mobile genetic elements detected.*\n\n")
}
```

```{r indiv_ge_summary, eval=!is_cohort}
if (!is.null(params$ge_summary_df) && nrow(params$ge_summary_df) > 0) {
  kable(params$ge_summary_df %>% select(Category, `Genes Detected` = n_genes),
        booktabs = TRUE, caption = "Genetic elements summary by database")
}
```

`r if (!is_cohort) '# 5. Alpha Diversity'`

```{r indiv_alpha_table, eval=!is_cohort}
if (!is.null(params$alpha_df) && nrow(params$alpha_df) > 0) {
  kable(params$alpha_df %>%
          select(Sample, `Sample Type` = type, Richness, `Shannon Index` = Shannon),
        booktabs = TRUE, align = c("l", "l", "c", "c"),
        caption = "Diversity metrics per sample")
}
```

```{r indiv_alpha_comparison, eval=!is_cohort, results='asis'}
if (!is.null(params$alpha_df) && nrow(params$alpha_df) > 0 &&
    !is.null(params$cohort_alpha_df) && nrow(params$cohort_alpha_df) > 0) {

  pat_mean_shan <- round(mean(params$alpha_df$Shannon, na.rm = TRUE), 2)
  pat_mean_rich <- round(mean(params$alpha_df$Richness, na.rm = TRUE), 0)
  coh_mean_shan <- round(mean(params$cohort_alpha_df$Shannon, na.rm = TRUE), 2)
  coh_mean_rich <- round(mean(params$cohort_alpha_df$Richness, na.rm = TRUE), 0)

  cat(paste0(
    "**Patient vs Cohort Comparison:**\n\n",
    "| Metric | This Patient | Cohort Average |\n",
    "|--------|:----------:|:-----------:|\n",
    "| Richness | ", pat_mean_rich, " | ", coh_mean_rich, " |\n",
    "| Shannon Index | ", pat_mean_shan, " | ", coh_mean_shan, " |\n\n"
  ))
}
```

`r if (!is_cohort) '# 6. Beta Diversity Context'`

```{r indiv_pcoa, eval=!is_cohort, fig.width=7, fig.height=5, out.width="100%"}
pd <- params$pcoa_data

if (!is.null(pd) && nrow(pd$pcoa_df) > 0) {
  ve <- pd$var_expl
  df <- pd$pcoa_df

  ggplot(df, aes(x = PC1, y = PC2,
                  colour = Immunodeficiency_diagnosis)) +
    geom_point(aes(size = highlight, alpha = highlight)) +
    scale_size_manual(values = c(`FALSE` = 1.5, `TRUE` = 4), guide = "none") +
    scale_alpha_manual(values = c(`FALSE` = 0.3, `TRUE` = 1), guide = "none") +
    stat_ellipse(linewidth = 0.7, linetype = "dashed") +
    scale_colour_manual(values = ip_palette) +
    labs(
      title = "PCoA - Patient Position in Cohort Context",
      subtitle = "Patient samples shown as larger points",
      x = paste0("PC1 (", round(ve[1], 1), "%)"),
      y = paste0("PC2 (", round(ve[2], 1), "%)"),
      colour = "Diagnosis"
    ) +
    eb_theme
}
```

```{r indiv_permanova, eval=!is_cohort, results='asis'}
if (!is.null(params$permanova_diag)) {
  perm_d <- params$permanova_diag
  cat(paste0(
    "**PERMANOVA (Diagnosis):** R\u00b2 = ", round(perm_d$R2[1], 4),
    ", F = ", round(perm_d$F[1], 2),
    ", p = ", perm_d$`Pr(>F)`[1], "\n\n"
  ))
}
if (!is.null(params$permanova_type)) {
  perm_t <- params$permanova_type
  cat(paste0(
    "**PERMANOVA (Sample Type):** R\u00b2 = ", round(perm_t$R2[1], 4),
    ", F = ", round(perm_t$F[1], 2),
    ", p = ", perm_t$`Pr(>F)`[1], "\n\n"
  ))
}
```

\vspace{1cm}
\noindent\textcolor{teal}{\rule{\textwidth}{1pt}}
\begin{center}
{\small\textcolor{gray}{Report generated on `r params$report_date` by E-Breathomics v0.1}}

\vspace{0.2cm}
{\footnotesize\textcolor{gray}{\textit{This report is intended for clinical use. All analyses are based on metagenomic sequencing data and should be interpreted in conjunction with clinical findings.}}}
\end{center}
